Reducing retrieval error in MAIAC AOD with the `Earth_obs_cleaning` machine-learning workflow: Results from CONUS

### 2023-01-04 writing/CONUS_AOD.Rmd
update YAML and Zotero library

---
title: "Running `Earth_obs_cleaning` on MCD19A2: Results from CONUS"
header-includes:
  - \usepackage{float}
  - \floatplacement{figure}{H}  #make every figure with caption = h, this was the fix
  - \usepackage{helvet} \renewcommand\familydefault{\sfdefault}
output_format:
  pdf_document: default
  html_document: default
always_allow_html: true
bibliography: references.json
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding,
  output_dir = "output", output_format = "all") })
---

>>>>

---
title: "Reducing retrieval error in MAIAC AOD with the `Earth_obs_cleaning` machine-learning workflow: Results from CONUS"
header-includes:
  - \usepackage{float}
  - \floatplacement{figure}{H}  #make every figure with caption = h, this was the fix
  - \usepackage{helvet} 
  - \renewcommand{\familydefault}{\sfdefault}
bibliography: references.json
csl: https://www.zotero.org/styles/atmospheric-measurement-techniques
output_format:
  html_document: default
always_allow_html: true
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding,
  output_dir = "output", output_format = "all") })
---
